Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-10-01 code/analysis.Rmd
updated plots

library(tidyverse)

@@

pumpfinal <- pump %>%
  filter(growth_days==0, date != 190417, dowel_density != "0232")

@@

### NEW ADDITION: Uncertainty propogation

@@

fitdata <- coefficients(fits) %>%
  mutate(k_t = -t) %>%
  cbind(dk_t = summary(fits)[[4]][,,'t'][,2], date = as.numeric(row.names(coefficients(fits)))) %>%
  left_join(metadata, by = "date")

fitdata %>%
  ggplot(aes(x = pump_freq, y = k_t, ymin = k_t - 1.96*dk_t, ymax = k_t + 1.96*dk_t, color = dowel_density)) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 3)) +
  geom_errorbar(width = 3, position = "dodge") +
  scale_color_hue(h.start = 0) +
  theme_minimal()

@@

Mixed feelings. On the one hand it's reassuring that aside from the switcharoo at 20 Hz, all runs with dowels had greater k_t than runs without. However, it seems like there's some serious variance. **What confounders could we be missing???**

@@

final %>%
  ggplot(aes(x = pump_freq, y = k_s, ymin = k_s - 1.96*dk_s, ymax = k_s + 1.96*dk_s, color = dowel_density)) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 3)) +
  geom_errorbar(width = 3, position = "dodge") +
  scale_color_hue(h.start = 0) +
  theme_minimal()

@@

If we're not using the $k_{tot}$ from the 20 Hz control, I think we should probably do the same with k_s, not least because it gives us linear $k_{bg}$ values, though this all still feels a little iffy.

Settling across the dowel treatments does seem to decrease, with a less clear pattern across flow velocity.

@@

final %>%
  filter(dowel_density != "0000") %>%
  ggplot(aes(x = pump_freq, y = k_c, ymin = k_c - 1.96*dk_c, ymax = k_c + 1.96*dk_c, color = dowel_density)) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 3)) +
  geom_errorbar(width = 3, position = "dodge") +
  scale_color_hue(h.start = 0) +
  theme_minimal()
```

Unlike the calculation with the measured values at the 20 Hz control, all k_c are in the green, but the pattern is still quite odd.

@@

final %>%
  filter(dowel_density != "0000") %>%
  ggplot(aes(x = pump_freq, y = eta, ymin = eta - 1.96*deta, ymax = eta + 1.96*deta, color = dowel_density)) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 3)) +
  geom_errorbar(width = 3, position = "dodge") +
  scale_color_hue(h.start = 0) +
  theme_minimal()

## Possible additions

- Turbulence data
    - The calculations are done 
    - But it might be good to include here for the sake of comprehensiveness

>>>>

library(tidyverse)
library(tikzDevice)

@@

pumpfinal <- pump %>%
  filter(growth_days==0, date != 190417, date != 190802, # leaving out old control 
         dowel_density != "0232")

@@

### Uncertainty propogation function: mutate_with_error

@@

fitdata <- coefficients(fits) %>%
  mutate(k_t = -t) %>%
  cbind(dk_t = summary(fits)[[4]][,,'t'][,2], date = as.numeric(row.names(coefficients(fits)))) %>%
  left_join(metadata, by = "date") %>%
  mutate(ad = as.numeric(dowel_density)*.003175^2, Re = pump_freq/500*.003175/9.509e-7)

fitdata %>%
  ggplot(aes(x = Re, y = k_t, ymin = k_t - 1.96*dk_t, ymax = k_t + 1.96*dk_t, color = as.character(round(ad,4)))) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 10)) +
  geom_errorbar(width = 10, position = "dodge") +  
  scale_color_manual(values = c("black","blue","green","red")) +
  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
  labs(y = expression(paste(italic(k[t])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
  theme_minimal()

@@

@@

final %>%
  ggplot(aes(x = Re, y = k_s, ymin = k_s - 1.96*dk_s, ymax = k_s + 1.96*dk_s, color = as.character(round(ad,4)))) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 10)) +
  geom_errorbar(width = 10, position = "dodge") +  
  scale_color_manual(values = c("black","blue","green","red")) +
  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
  labs(y = expression(paste(italic(k[s])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
  theme_minimal()

@@

$k_s$ seems negatively related to both dowel density and flow velocity.

@@

final %>%
  filter(dowel_density != "0000") %>%
  ggplot(aes(x = Re, y = k_c, ymin = k_c - 1.96*dk_c, ymax = k_c + 1.96*dk_c, color = as.character(round(ad,4)))) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 10)) +
  geom_errorbar(width = 10, position = "dodge") +  
  scale_color_manual(values = c("blue","green","red")) +
  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
  labs(y = expression(paste(italic(k[c])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
  theme_minimal()
```

@@

final %>%
  filter(dowel_density != "0000") %>%
  ggplot(aes(x = Re, y = eta, ymin = eta - 1.96*deta, ymax = eta + 1.96*deta, color = as.character(round(ad,4)))) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 10)) +
  geom_errorbar(width = 10, position = "dodge") +  scale_color_manual(values = c("blue","green","red")) +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Effective capture efficiency", x = expression(Re[c]), color = expression(italic(ad))) +
  theme_minimal()
```
